PM Mungbean meta-analysis

### 2021-03-01 02_Preliminary_analysis.Rmd
Delete unused function

### Disease pressure  
The amount of disease pressure between seasons is another variable which could impact mungbean yield meta-analysis effect size. 
```{r D_pres}
# Assess the effect of yield pressure on the spray schedule efficacy
PM_MB_dat[,"trial_ref"]

mean_control <- function(trial) {
   mean(PM_MB_dat[PM_MB_dat$trial_ref == trial &
               PM_MB_dat$fungicide_ai == "control", "grain_yield.t.ha."], na.rm = TRUE)
}

PM_MB_dat$Y_control <- sapply(PM_MB_dat$trial_ref, mean_control)

# Quantile to separate disease pressure
DP33 <- 
   PM_MB_dat %>%
   filter(fungicide_ai == "control") %>%
   pull(PM_final_severity) %>%
   quantile(0.3333)

>>>>

### Disease pressure  
The amount of disease pressure between seasons is another variable which could impact mungbean yield meta-analysis effect size. 
```{r D_pres}
# Assess the effect of yield pressure on the spray schedule efficacy
# Quantile to separate disease pressure into High, Medium and low disease pressure categories
DP33 <- 
   PM_MB_dat %>%
   filter(fungicide_ai == "control") %>%
   pull(PM_final_severity) %>%
   quantile(0.3333)
